---
title: "Practice 6.1"
author: "Arnaud Guerbet"
date: "2022-10-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lotka- Volterra equation

Definition of the model "grow" with fix competition coefficients (a12=0.8; a21=0.8), carrying capacities (K1=100, K2=120) and a number of generation of 30. 
Growth rate of two species need to be defined. 

```{r cars}
grow<-function(start_1,start_2,growth.rate1,growth.rate2){
  num_gen<-30
  N1 <- rep(1,num_gen)
  N2 <- rep(1,num_gen)
  generation<-rep(0,num_gen)
  grw.rt1<-growth.rate1
  grw.rt2<-growth.rate2
  K1<-100
  K2<-120
  a12<-0.8
  a21<-0.8
  N1[1]<-start_1
  N2[1]<-start_2
  generation<-1:num_gen
  
  for (i in 2:num_gen)  {
    N1[i] = N1[i-1] + (grw.rt1* N1[i-1] * ((K1-N1[i-1]-(a12*N2[i-1]))/K1))
    N2[i] = N2[i-1] + (grw.rt2* N2[i-1] * ((K2-N2[i-1]-(a21*N1[i-1]))/K2))
  } 
  
  if (N1[1]>0.5 && N2[1]<0.5){
    plot(N1~generation,typ="b",ylim=c(0,K1+20),ylab="N")}  
  
  if (N1[1]<0.5 && N2[1]>0.5){
    plot(N2~generation,typ="b",ylim=c(0,K2+20),ylab="N")}
  
  if (N1[1]>0.5 && N2[1]>0.5){
    plot(N2~generation,typ="b",ylim=c(0,max(c(K1+20,K2+20))),ylab="N")
    lines(N1~generation,typ="b",col=2)}
}
```

## Plots of the model

First plot for N1 only (smart_1=1), second one for N2 (smart_2=1) and the last one for the interaction between N1 and N2 (smart_1=1;smart_2=1).
Growth.rate1 is defined by 1.5 and Growth.rate2 by 0.8.

```{r pressure, echo=FALSE}
par(mfrow=c(3,1),las=1)

grow(1,0,1.5,0.8)
text(15,50,"Species 1 alone")

grow(0,1,1.5,0.8)
text(15,60,"Species 2 alone")

grow(1,1,1.5,0.8)
text(6,120,"Both Species competing")
```


